---
title: "Quick peak into functional relations between predictors and an outcome."
author: Ignat Drozdov
date: March 10, 2017
output:
  md_document:
      variant: markdown_github
---

# Motivation
Black box prediction methods like random forests and neural networks form the backbone of many computational analyses. Nevertheless, it can be difficult to understand functional relationships between predictors and outcome when decision rules are not explicitly stated.

A number of approaches have been introduced to help researchers peak into black box models to get a better understanding of its inner workings. Some examples are:

* Local Interpretable Model-Agnostic Explanations (LIME) - [python](https://github.com/marcotcr/lime) and [R](https://github.com/thomasp85/lime) code.

* Partial Dependency Plots - [R](https://github.com/bgreenwell/pdp) code.

* Individual Conditional Expectation (ICE) - [R](https://github.com/kapelner/ICEbox) code.

**quickpeak** does not attempt to replace any of these algorithms. In fact, the package offers only a very rough estimate of Partial Dependency Plots and is not suitable for rigurous analysis. The main focus of the package is on computational speed in large datasets.

# Approach

Values of each feature that is being assessed are held unchanged. For all other predictors, **quickpeak** takes the median value of continuous variables and the first level for all factors. Posterior class probabilities are then computed on this new dataset.

For each observation in the feature of interest **quickpeak** reports the odds as given by:

**p**/(1-**p**), where **p** is class probability vector.

# Installation

The latest version can be installed through:

```{r, eval=FALSE}
devtools::install_github("beringresearch/ABC/quickpeak")
```

# Example

```{r}
library(quickpeak)
library(ranger)

model <- ranger(data=iris, dependent.variable.name="Species", probability=TRUE)

# Ranger's implementation of the predict function is not standard.
# We create our own and pass it to quickpeak.

custom_predict <- function(model, newdata){
	predict(model, newdata)$predictions
}

# Note that we must exclude the column that contains our outcome vector
# from the training dataset prior to passing it to qpeak.

qp <- qpeak(model=model, X=iris[,-5], feature="Sepal.Length", predict=custom_predict)

head(qp)

```

The function returns odds such that higher values indicate greater affinity towards output of interest. We can now visualise the "decision vector" in our iris model.

```{r}
plot(qp, pch=19, col=iris$Species)
```
