---
title: "Machine Learning Version Control for R"
author: Ignat Drozdov
date: October 29, 2017
output:
  md_document:
        variant: markdown_github
---


# Installation

The latest version can be installed through:

```{r, eval=FALSE}
devtools::install_github("beringresearch/ABC/mlvc")
```

# Examples
Let's start by building a 100 tree Random Forest model using the Iris dataset and commiting it to MLVC repository.

```{r, eval=TRUE}
library(mlvc)
library(randomForest)

rf <- randomForest(Species~., data = iris, ntree = 100)
rf

ml_add(model = rf, X = iris, Y = NULL, repo = "iris", comment = "Random Forest model with 100 trees")
```

```{r, eval = TRUE, include = FALSE}
Sys.sleep(10)
```

*ml_add* requires a model, training set, response variable, repository title, and a brief commit message. All variables are serialised and inserted into a local SQLite database.

Let's retrain the Random Forest model, increasing the number of trees.

```{r, eval=TRUE}
rf <- randomForest(Species~., data = iris, ntree = 500)
rf

ml_add(model = rf, X = iris, Y = NULL, repo = "iris", comment = "Random Forest model with 500 trees")
```

Our __iris__ repository should contain two models with 100 and 500 trees respectively:

```{r, eval=TRUE}
ml_list()
```

Each model is has a unique identifier that relates directly to its creation time stamp. To access the model:

```{r, eval=TRUE}
object <- ml_checkout(repo = "iris", version = names(ml_list()$iris)[2])
object
```
