---
title: "Improved visualisations of machine learning model performances"
author: Ignat Drozdov
date: November 9, 2017
output:
  md_document:
        variant: markdown_github
---


# Installation

The latest version can be installed through:

```{r, eval=FALSE}
devtools::install_github("beringresearch/ABC/confused")
```

# Examples

## Squares
Squares is a visualisation technique developed by Microsoft to [support interactive performance analysis for multiclass classifiers](https://www.microsoft.com/en-us/research/publication/squares-supporting-interactive-performance-analysis-multiclass-classifiers/). Squares facilitates display of instance level distribution information, which is necessary for informative model selection and hyperparameter tuning.

```{r}
library(confused)
library(rpart)
library(mlbench)

data(Soybean)
Soybean$Class <- as.factor(as.numeric(Soybean$Class))
levels(Soybean$Class)

dim(Soybean)
```

Let's built a simple Rpart classifier:

```{r}
Y <- Soybean[, 1]

set.seed(123)
trainIndex <- sample(seq_len(nrow(Soybean)), size = round(0.75 * nrow(Soybean)), replace = FALSE)

train <- Soybean[trainIndex, ]
test <- Soybean[-trainIndex, ]

model <- rpart(Class~., data = train)
yh <- predict(model, test)
```

Finally, visualise performance:

```{r squares-vis, fig.height=4, fig.width=9}
squares(yh, test$Class)
```

All classes are represented with facets, whilst frequency distribution of probability estimates of each class instance is visualised as a histogram. It can be seen that our model is excellent in predicting classes _7_, _9_, _10_, and _17_.


## Beads
Similar approach as the Squares plot, but each class is visualised along a vertical axis to facilitate cross-class comparisons.

```{r}
beads(yh, test$Class)
```

## Confusion Matrix
A graphical representation of a confusion matrix. We retain class probabilities generated in previous section.

```{r confusion-matrix, fig.height = 6, fig.width = 9}
lbl <- colnames(yh)[apply(yh, 1, which.max)]
confusion_matrix(lbl, test$Class)
```
